---
title: "Homework 1"
output: github_document
---

First, I need to load the package that I need for for data construction and manipulation. Here is the **code chunk** for loading package. 

```{r}
library(tidyverse)
```


# Problem 1

This problem focuses on variable types and coercion. Here's a **code chunk** that construct the data frame, which includes random sample, logical vector, character vector and factor vector :

```{r data frame}
p1data = tibble(
  vec_numeric = runif(10, min=0, max=5),
  vec_char = c("a", "b", "c", "d","e","f","g","h","i","j"),
  vec_factor = factor(c("male", "male", "female", "female","male", "male", "female", "female","male", "male")),
  vec_logical = as.logical(vec_numeric>2)
)

class(p1data$vec_logical)
```

After constructing the data, we are asked to take the mean of each variable in your dataframe. The mean of numerical vector, the random sample from a uniform[0, 5] distribution is `r mean(p1data$vec_numeric)`. The mean of the logical vector, which indicates whether elements of the sample are greater than 2, is `r mean(p1data$vec_logical)`. On the other hand, the means of the factor vector and the character vector are both`r mean(p1data$vec_factor)` and `r mean(p1data$vec_char)`. The logical vector has a mean because it is recognized as "0" and "1", however, the factor vector and charater vector are not numerical values.