---
title: "Homework 1"
output: github_document
---

First, I need to load the package that I need for for data construction and manipulation. Here is the **code chunk** for loading package. 

```{r}
library(tidyverse)
```


# Problem 1

This problem focuses on variable types and coercion. Here's a **code chunk** that construct the data frame, which includes random sample, logical vector, character vector and factor vector :

```{r data frame}
p1data = tibble(
  vec_numeric = runif(10, min=0, max=5),
  vec_char = c("a", "b", "c", "d","e","f","g","h","i","j"),
  vec_factor = factor(c("male", "male", "female", "female","male", "male", "female", "female","male", "male")),
  vec_logical = as.logical(vec_numeric>2)
)

```

After constructing the data, we are asked to take the mean of each variable in your dataframe. The mean of numerical vector, the random sample from a uniform[0, 5] distribution is `r mean(p1data$vec_numeric)`. The mean of the logical vector, which indicates whether elements of the sample are greater than 2, is `r mean(p1data$vec_logical)`. On the other hand, the means of the factor vector and the character vector are both `r mean(p1data$vec_factor)` and `r mean(p1data$vec_char)`. The logical vector has a mean because it is recognized as "0" and "1", however, the factor vector and charater vector are not numerical values.

We are then asked to explicitly convert variables from one type to another. Here is the **code chunk** to convert logical, character, and factor variables to numerical values. 

```{r, message = FALSE, warning = FALSE}
p1_log_to_num = as.numeric(p1data$vec_logical)
p1_fac_to_num = as.numeric(p1data$vec_factor)
p1_char_to_num = as.numeric(p1data$vec_char)
```

The logical vector are converted to "1" and "0" as numerical values and the factor vector are converted to "1" and "2" as numerical values. On the other hand, for the charater vecter, NAs are introduced by coercion. 

Finally, we are going to convert our character variable from character to factor to numeric; similarly, convert our factor variable from factor to character to numeric. Here is the **code chunk** 

```{r, message = FALSE, warning = FALSE}
p1_char_to_fac_to_num = as.numeric(as.factor(p1data$vec_char))
p1_fac_to_char_to_num = as.numeric(as.character(p1data$vec_factor))
```

The charater variable that converted to factor and then to numeric were shown as "1", "2", "3" to "10". It is because the 10 charaters are converted to factors first, then it has 10 different factors. When the 10 different factors are converted to numerical values, they are shown as 10 integers. For the factor variable, it was converted to charater first and when charaters are converted to numerical values, NAs are introduced by coercion. 

# Problem 2

This problem focuses on plotting and the use of inline R code. Here's a **code chunk** that construct the data frame, which includes two random samples, logical vector, character vector and factor vector

```{r}
p2data = tibble(
  x = rnorm(1000,mean=0),
  y = rnorm(1000,mean=0),
  vec_logical = as.logical(x + y >0),
  Log_to_num_coer = as.numeric (vec_logical),
  Log_to_fac_coer = as.factor(vec_logical)
)
```

